Tulai

### 2023-09-16 paper/paper_tulai.qmd
summary table edited

```{r}
# Generate a summary table by grouping by 'depth'
summary_table_depth_tool_type <- tl_final %>%
  group_by(depth) %>%
  summarise(tool_type = n_distinct(tooltypegroup))

# Create a full summary table by joining it back to your original summary table based on 'depth'
summary_table_depth_area_layer <- summary_table_depth_area_layer %>%
  left_join(summary_table_depth_tool_type, by = "depth")

# Print column names 
print(names(summary_table_depth_area_layer))

>>>>

```{r}
# Generate a summary table by grouping by 'depth' and 'area'
summary_table_depth_tool_type <- tl_final %>%
  group_by(area, depth) %>%
  summarise(tool_type = n_distinct(tooltypegroup, na.rm = TRUE))

# Create a full summary table by joining it back to original summary table based on 'depth' and 'area'
summary_table_depth_area_layer <- summary_table_depth_area_layer %>%
  left_join(summary_table_depth_tool_type, by = c("area", "depth"))
